---
title: "[`iosp`](https://github.com/koncina/iosp) ioslides plus"
author: "Eric Koncina, Aurélien Ginolhac"
date: "11/29/2016"
output:
  iosp::ioslides_plus:
    fig_height: 5
    fig_width: 6
    keep_md: no
    logo: img/uni.png
    smaller: yes
    widescreen: yes
    self_contained: false
    lib_dir: libs
    fig_retina: null
---

## bootstrap layout

A row is defined with `<div class = "row stretch">`. **Strech** so all defined box have the same height

<div class = "row stretch">
<div class = "col-6 box bg-red ">
### Warning
based on bootstrap, this a box of width 6

`<div class = "col-6 box bg-red ">`

</div>
<div class = "col-6 box bg-green">
### green
another box of width 6

#### green is the color with 4 hashes

**bold** : _italic_
</div>
</div>
<div class = "row">
<div class = "col-5 box bg-yellow">
### 3 hashes`###` makes a title
here is a class "col-5 box bg-yellow"
</div>
<div class = "col-5 box bg-blue">
### blue note
class "col-5 box bg-blue", summing to 12 is optional
</div>
</div>

Below, defined another `row`
<div class = "row">
<div class = "col-10 box">
A simple box, no background `<div class = "col-10 box">`
</div>
</div>

<div class = "row">
<div class = "col-3">
</div>
<div class = "col-9">
before a `div class = "col-3` and here a `div class = "col-9"`
</div>
</div>

## R code | subtitle on the rigth to save space

<div class = "row stretch">
<div class = "col-7 box bg-yellow">
### fav regression, yellow bg

```{r}
lm(mpg ~ poly(wt, 2), data = mtcars)
```

Syntax is highligthed _à la_ [Rstudio](https://www.rstudio.com/)

</div>
<div class = "col-5 box">
### plot in  a box 
```{r, message = FALSE, fig.height = 3, fig.width = 3.5}
library(tidyverse)
ggplot(mtcars, aes(mpg, wt)) +
  geom_point() +
  geom_smooth(method = "lm", 
              formula = y ~ poly(x, 2))
```
</div>
</div>


## Install from github {.vs1} (add 1 vertical space with `{.vs1}`)


### R package 

by [Eric Koncina](https://github.com/koncina) install with [`devtools`](https://cran.r-project.org/web/packages/devtools/index.html):


```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("koncina/iosp")
```


### YAML header for this presentation
```{r, eval = FALSE}
---
iosp::ioslides_plus:
  keep_md: no
  logo: img/uni.png
  smaller: yes
  widescreen: yes
  self_contained: false
  lib_dir: libs
  fig_retina: null
---
```
</div>

### Rmarkdown code

[here on github](https://github.com/ginolhac/iosp_demo/blob/master/iosp.Rmd)

## session info

```{r}
devtools::session_info()
```

